Wrinkling of a confined porous layer

### 2014-05-27 poster_Okinawa.tex
Introduces epsilon

\begin{tikzpicture}[ultra thick]
\begin{axis}[
	name=a,
	width=\textwidth, height=0.25\textwidth, scale only axis,
	domain=-180:180, no markers, ymin=0, ymax=4,xmin=-180,xmax=180,
	axis lines=none, xtick=\empty,
	]
	\addplot+[Accent1]{cos(x)+1};
	\addplot+[Accent1]{cos(x)+1.5};
	\draw[->, ultra thick] (axis cs:90,1.25) -- +(45:0.05\textwidth) node[pos=1, above] {$\vec{v}$};
	\node[above] at (axis cs:-90,1.5) {$P_2$};
	\node[below right] at (axis cs:-90,1.25) {$P_1$};
\end{axis}
\fill[pattern=north east lines,pattern color=Accent2] (a.south west) rectangle (\textwidth,-1em);
\draw[<->] ($(a.south west)+(0,-1.1em)$) -- +(\textwidth,0) node[midway, below] {$\lambda$};
\end{tikzpicture}

\begin{itemize}
\item Synæresis then swelling
\item First blister after $\approx\SI{1}{\hour}$ of swelling
\item Independent blisters
\item $\lambda \ll L \Rightarrow$ not buckling
\item Once in contact with ceiling, $\lambda$ fixed
\item Cascade buckling\linebreak \hfill\textit{Roman \& Pocheau 1999}
\end{itemize}
\end{textblock}

\begin{textblock}{3}(8,8.5)
Bending energy $B$ vs vertical stress $\sigma$:
\[ \lambda^* = \left(\frac{B}{\sigma}\right)^{1/3}\text{, eg. }\sigma =\rho g h \]
\textit{Kolinski et al 2009, Vella et al 2009}

Here $\sigma$ is a Darcy pressure due to solvent flow through the gel (pore size $\ell_p$)
\[\sigma = \Delta P \sim \eta h v/\ell_p^2   \]
\end{textblock}

>>>>

\begin{tikzpicture}[ultra thick]
\begin{axis}[
	name=a,
	width=\textwidth, height=0.25\textwidth, scale only axis,
	domain=-180:180, no markers, ymin=0, ymax=4,xmin=-180,xmax=180,
	axis lines=none, xtick=\empty,
	]
	\addplot+[Accent1]{cos(x)+1};
	\addplot+[Accent1]{cos(x)+1.5};
	\draw[->, ultra thick] (axis cs:90,1.25) -- +(45:0.05\textwidth) node[pos=1, above] {$\vec{v}$};
	\node[above] at (axis cs:-90,1.5) {$P_2$};
	\node[below right] at (axis cs:-90,1.25) {$P_1$};
	\draw[<->, ultra thick] (axis cs:0,0) -- (axis cs:0,2) node[midway, right] {$A$};
\end{axis}
\fill[pattern=north east lines,pattern color=Accent2] (a.south west) rectangle (\textwidth,-1em);
\draw[<->] ($(a.south west)+(0,-1.1em)$) -- +(\textwidth,0) node[midway, below] {$\lambda$};
\end{tikzpicture}

\begin{itemize}
\item Synæresis then swelling
\item First blister after $\approx\SI{1}{\hour}$ of swelling
\item Independent blisters
\item $h,H,e \ll \lambda \ll L$
\item Once in contact with ceiling, $\lambda$ fixed
\item Cascade buckling\linebreak \hfill\textit{Roman \& Pocheau 1999}
\item Independent of gravity
\end{itemize}
\end{textblock}

\begin{textblock}{3}(8,8.5)
\Subhead{Ruck in a rug analogy}\\
\textit{Kolinski et al 2009, Vella et al 2009}\\
Bending energy $B$ vs vertical stress $\sigma$:
\[ \lambda^* = \left(\frac{B}{\sigma}\right)^{1/3}\text{, eg. }\sigma =\rho g h \]

Actual shape depends on relative excess length $\epsilon$: $\lambda \sim \epsilon^{1/7} \lambda^*$ and $A \sim \epsilon^{4/7} \lambda^*$

\Subhead{Poroelasticity}\\
Here $\sigma$ is a Darcy pressure due to solvent flow through the gel (pore size $\ell_p$)
\[\sigma = \Delta P \sim \eta h v/\ell_p^2   \]
\end{textblock}
